On the probability of finding a nonphysical solution through shadowing

### 2020-10-27 main.tex
emphasize smallness of perts

Through a rigorous counter-example, we show that shadowing can lead
to nonphysical solutions. This has a troubling implication for numerical simulations of chaotic
governing equations.  Through the examples in this paper, it is clear that a numerical solution, satisfying
a governing equation perturbed due to numerics, is not 
expected to be shadowed by a
physical solution of the real governing physics.  What is, if any, the
relation of a numerical solution, such as DNS of turbulent flows, to
the true physics? For an ${\cal O}(10^{-18})$ 
perturbation (due to numerical error), 
we may get completely different statistics from a true, physical solution. How then can we trust numerical solutions when they are not guaranteed to share the long-term statistical behavior of the governing equation? 
We conclude with an example that illustrates a counterintuitive feature of some chaotic systems: a small perturbation to the 
governing equation can significantly change the statistics/long-term 
behavior of its physical solutions. We construct yet another 
perturbed tent map -- the \emph{plucked} 
tent map -- in which an oscillatory perturbation is introduced (see Supplementary Material section \ref{sec:pluckedTentMap} for the map equation). In Figure \ref{fig:pluckedTentMap}, we show that the magnitude of the oscillatory perturbation is controlled by a parameter $s$, and its frequency is controlled by the parameter $n$; at $s=0,n=0$, we recover the original tent map. The stationary probability distributions -- computed empirically over a trajectory of length 10 billion -- at $s=0.1$, are shown in Figure \ref{fig:pluckedTentMapDistribution}. On the left, $n=0$ and there is already a marked asymmetry developed in the probability distribution compared to the uniform distribution seen at $s=0, n=0$. On the right, we show that by increasing $n,$ despite the fact that the magnitude of the perturbation remains small, we see a dramatic change in the appearance of the stationary probability distribution: we observe an apparent fractal distribution reminiscent of that of the quasi-physical solutions in 
section \ref{sec:tentPerts}. By construction of the map (Supplementary Material section \ref{sec:pluckedTentMap}), the nonuniformities of the probability distribution at $n=0$ are transferred to smaller and smaller scales, 
as $n$ is increased. Although this effect is more pronounced as $s$, and hence the magnitude of the perturbation, is increased, it must be emphasized that remarkable changes in the physical distribution can be effected, by applying even a small perturbation.

>>>>

Through a rigorous counter-example, we show that shadowing can lead
to nonphysical solutions. This has a troubling implication for numerical simulations of chaotic
governing equations.  Through the examples in this paper, it is clear that a numerical solution, satisfying
a governing equation perturbed due to numerics, is not 
expected to be shadowed by a
physical solution of the real governing physics.  What is, if any, the
relation of a numerical solution, such as DNS of turbulent flows, to
the true physics? For an ${\cal O}(10^{-18})$ 
perturbation (due to numerical error), 
we may get completely different statistics from a true, physical solution. How then can we trust numerical solutions when they are not guaranteed to share the long-term statistical behavior of the governing equation? 
We conclude with an example that illustrates a counterintuitive feature of some chaotic systems: a small perturbation to the 
governing equation can significantly change the statistics/long-term 
behavior of its physical solutions. We construct yet another 
perturbed tent map -- the \emph{plucked} 
tent map -- in which an oscillatory perturbation is introduced (see Supplementary Material section \ref{sec:pluckedTentMap} for the map equation). In Figure \ref{fig:pluckedTentMap}, we show that the magnitude of the oscillatory perturbation is controlled by parameters $s$ and $n$, and its frequency is controlled by the parameter $n$; at $s=0,n=0$, we recover the original tent map. The stationary probability distributions -- computed empirically over a trajectory of length 10 billion -- at $s=0.1$, are shown in Figure \ref{fig:pluckedTentMapDistribution}. On the left, $n=0$ and there is already a marked asymmetry developed in the probability distribution compared to the uniform distribution seen at $s=0, n=0$. On the right, we show that by increasing $n,$ despite the fact that the magnitude of the perturbation becomes smaller with $n$, we see a dramatic change in the appearance of the stationary probability distribution: we observe an apparent fractal distribution reminiscent of that of the quasi-physical solutions in 
section \ref{sec:tentPerts}. By construction of the map (Supplementary Material section \ref{sec:pluckedTentMap}), the nonuniformities of the probability distribution at $n=0$ are transferred to smaller and smaller scales, 
as $n$ is increased. It is worth emphasizing that remarkable changes in the physical distribution are effected (as shown in the right hand side of Figure \ref{fig:pluckedTentMapDistribution}) with a tiny perturbation -- the perturbed map at $n=10$, and the original tent map appear indiscernible on the left hand side of Figure \ref{fig:pluckedTentMap}.
